Labour Market Resilience

### 2024-03-12 outputs/paper/paper.qmd
update appendix

>>>>

Welcome to our survey, which builds on our research analyzing the impact of economic downturns on labour dynamics in the U.S. from 1972 to 2022, based on the General Social Survey (GSS). The GSS collects information and historical records of respondents' attitudes and experiences. Our study has highlighted significant shifts in working hours, particularly during crises such as the 2008 Financial Crisis and the COVID-19 pandemic, affecting various demographic groups differently. This survey seeks to deepen our understanding of these impacts and gather more nuanced data on labour force participation across different economic conditions.

Your participation is voluntary and confidential. You may skip any question or withdraw at any time. Responses are anonymized and will be used solely for research purposes. For any inquiries or additional information, please contact us at evan.hao@mail.utoronto.ca, mingjia.chen@mail.utoronto.ca, and/or catherine.punnoose@mail.utoronto.ca.

## Survey Questions
\begin{itemize}
        \item Demographic Information:
            \begin{enumerate}
                \item What is your age group?
                \begin{itemize}
                  \item Under 18
                  \item 18-24
                  \item 25-34
                  \item 35-44
                  \item 45-54
                  \item 55-64
                  \item 65+
                \end{itemize}
                \item What is your highest level of education?
                \begin{itemize}
                  \item High school graduate
                  \item Bachelor's degree
                  \item Graduate or professional degree
                \end{itemize}
                \item Please specify your gender:
                \begin{itemize}
                  \item Male
                  \item Female
                  \item Non-binary
                  \item Prefer not to say
                \end{itemize}
            \end{enumerate}
        \item Employment Status and Industry:
              \begin{enumerate}
                \item What is your current employment status?
                \begin{itemize}
                  \item Employed full-time
                  \item Employed part-time
                  \item Unemployed
                  \item Retired
                  \item Student
                \end{itemize}
                \item If employed, what industry do you work in?
                \begin{itemize}
                  \item Manufacturing
                  \item Construction
                  \item Retail
                  \item Hospitality
                  \item Healthcare
                  \item Education
                  \item Information Technology
                  \item Professional Services
                  \item Other (please specify)
                \end{itemize}
            \end{enumerate}
        \item Impact of Economic Downturns:
              \begin{enumerate}
                \item How did the 2008 financial crisis and/or the COVID-19 pandemic affect your working hours? Did your hours:
                \begin{itemize}
                  \item Increase
                  \item Decrease
                  \item Stay the same
                  \item Not applicable/I wasn't employed during these times
                \end{itemize}
                \item Did you have to switch to remote work during the COVID-19 pandemic?
                \begin{itemize}
                  \item Yes
                  \item No
                  \item Not applicable
                \end{itemize}
              \end{enumerate}
        \item Responses to Economic Downturns:
              \begin{enumerate}
                \item In times of economic downturn, what support measures do you believe are most effective for workers?
                \begin{itemize}
                  \item Unemployment benefits
                  \item Skills retraining programs
                  \item Direct financial aid
                  \item Flexible work arrangements
                  \item Other (please specify)
                \end{itemize}
            \end{enumerate}
\end{itemize}
